Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-07-10 demystify.tex
updates

    \item Miscs and FAQS
        \begin{itemize}
          \item Why you were rejected (\autoref{sec:why-rejected}). One potential reason is because you're applying to AI/ML, a super competitive field in recent years with many applicants.

>>>>

    \item Miscs and FAQS
        \begin{itemize}
          \item One reason why you were rejected (\autoref{sec:why-rejected}) is because you applied to AI/ML, a super competitive field in recent years with many applicants.
